Inference methods comparison for the simplified Naomi model

### 2023-02-21 src/naomi-simple_compare/comparison.Rmd
Add outcome placeholder, and graphs for worst nodes

# KS plots

@@

@@

>>>>

## Outcome variables

These are the outcome variables which we might be interested in to monitor:

```{r}
names(tmb$fit$sample)[!(names(tmb$fit$sample) %in% pars)]
#' To-do: elicit from Jeff in particular which of these we should be focusing on the posterior output of
#' Guess would be the indicators HIV prevalence (rho_t1_out), ART coverage (alpha_t1_out), HIV incidence (lambda_t1_out)
```
# KS plots

@@

```{r}
histogram_and_ecdf(par = "u_alpha_xs", i = 18)
histogram_and_ecdf(par = "u_alpha_xs", i = 29)
histogram_and_ecdf(par = "ui_anc_alpha_x", i = 29)
```

@@

```{r}
histogram_and_ecdf(par = "log_or_gamma", i = 18)
histogram_and_ecdf(par = "ui_anc_rho_x", i = 10)
histogram_and_ecdf(par = "log_or_gamma", i = 1)
```
